
\input{./LaTeX_configuration/packagePreamble.sty}
\input{./LaTeX_configuration/formattingPreamble.sty}
\input{./LaTeX_configuration/mathPreamble.sty}
\input{./LaTeX_configuration/header.tex}

% The command structure is as follows:
% \headerfooter{ Class/Course }[optional: problem set, assignment, homework]{ number of problem set }{ due date }[Name]
\headerfooter{}[Final Project]{}{12/06/2018}[Annan Deng, John Canty, Ramasubramanian Balasubramanian, William Krinsman]

% creation of code font following guidelines found here: https://tex.stackexchange.com/a/36031/103825
\newcommand{\code}[1]{\mbox{\texttt{#1}}}

% when the problems you have to answer begin in section 2, uncomment this:
% \setcounter{section}{1}

% don't want this formatting style in the general template for all classes, 
% but do want these assignments to follow her  page format
\renewcommand{\thesubsection}{ \arabic{subsection}.}
\renewcommand{\thesubsubsection}{(\alph{subsubsection})}

\begin{document}

%You can fill in your name in the bracket below and it will print the header HW with your name in it
% In particular the command structure is as follows:
% \HW{ Class/Course }[optional: problem set, assignment, homework]{ number of problem set }{ due date }[Name]
%\HW{PH 240C}[Final Project]{}{12/06/2018}[Ramasubramanian Balasubramanian, John Canty, Annan Deng, William Krinsman]

\title{PH240C Final Project \break\break {\Huge Protein Expression across Disease Groups:} \break \break {\Huge Analysis of the Human Brain Proteome} }
\date{December 6th, 2018}
\author{Ramasubramanian Balasubramanian, John Canty, Annan Deng, William Krinsman}

\maketitle

\section*{Abstract}
\label{sec:abstract}
\addcontentsline{toc}{section}{Abstract}



\pagebreak

\tableofcontents

\pagebreak

\section{Introduction}
\label{sec:introduction}

Patients with neurodegenerative disorders such as Alzheimer’s disease (AD) and Parkinson’s disease (PD) share common physiological and symptomatic similarities, however the molecular pathways linking these diseases are incompletely understood. Recently, a comprehensive quantitative proteomic dataset of the human brain in patients with AD, PD, and AD/PD comorbidity has been publicly released. We will perform exploratory data analysis and modelling in order to identify if there are disease-specific differential gene expression patterns that are associated with AD and PD neuropathologies. We will then perform Weighted Correlation Network Analysis (WCNA) of the identified genes to assess if there coexpression relationships between subsets of these genes. Finally, using the PANTHER gene ontology classification system, we will assess whether these genes exhibit functional relationships. 



\section{Dataset}
\label{sec:dataset}

The dataset\cite{proteome} that we will be evaluating was obtained by performing Tandem Mass Tag (TMT) isobaric mass spectrometry on brain tissue obtained from individual human donors. Brain tissue samples were obtained from $40$ individual patient samples across two separate brain regions, the Frontal Cortex and the Anterior Cingulate Gyrus). The dataset obtained by using a factorial experimental design, where there are $5$ experimental batches, with two samples of each phenotype (Control Patient, Alzheimer’s Patient, Parkinson’s Patient, Alzheimer’s/Parkinson’s Patient) within each batch. For each batch, a control sample was generated by pooling fractions of all samples in order to generate a global internal standard (GIS) expression measure. Individual data entries are displayed as base-$10$ log-transformed ratios of the obtained peptide counts for the $ij$th sample covariate of interest and the $i$th covariate of the GIS standard. From the Frontal Cortex, $10,100$ unique protein groups were identified, while from the Anterior Cingulate Gyrus, $10,695$ protein groups were identified.

\section{Exploratory analysis and preprocessing}
\label{sec:expl-analys-prepr}

 In the initial portion of this project, we will assess data quality, phenotype and  inter-batch variability by box-plot visualization. We will then assess the raw data and apply quantile normalization samples. Finally, we assess the whether or not disease-trait groups can be discriminated based on gene expression values by applying dimensionality reduction methods. 

\subsection{Data quality and Preprocessing}
\label{subsec:data-qual-vari}

We performed several quality control steps on the data-set before analysis. A large fraction of the gene rows contained batches that consisted of entirely NA or zero values that needed to be removed. We attribute these values to commonly reported issues of label-free mass spectrometry experiments that involve probe bias and reduced coverage of peptides. In order to preserve genes that contained peptide counts for all batches, we removed any gene that had NAs present in any batch. Next, we repeated the process by removing any gene that contained zeros, since these values would result in undefined log-transformed expression measures. In the Frontal Cortex, this process resulted in a final gene count of $6,004$ from an original dataset of $10,100$ genes. In the Anterior Cingulate Gyrus, this resulted in a final gene count of $6230$ genes. 

\subsection{Exploratory analysis}
\label{subsec:exploratory-analysis}

In order to assess our processed data, we visualized the distribution of all fold-change (FC) gene expression values for each patient sample across all disease traits (Ctl, AD, PD, and ADPD) \textbf{ (Fig.1A)}. Upon inspection of the plots, we noticed that all samples had FC gene expression values that were centered around zero, indicating that the experimental effects between batches were significantly reduced by normalizing against a GIS for each batch. However, for a fraction of patient samples, we still observed significant FC gene expression outliers. 

Next, we performed Principle Component Analysis (PCA) on the samples in both the Frontal Cortex and the Anterior Cingulate Gyrus \textbf{(Fig.2A and B)}. A PCA plot of all disease traits did not indicate any clear separation of classes in both tissues. In order to simplify visualization, we then generated pairwise PCA plots between the Control samples and disease-state samples in both tissues \textbf{ (Fig.2C and D)}. In both tissue samples, we observed that clear separation of the Control and AD samples. Similarly, we observed separation of the Control and comorbid ADPD samples. However, when when we analyzed the Control and PD samples, we did not observe clear separation between the two traits.

We then quantitatively assessed the separation between the Control and disease-state samples by applying a Support Vector Machine (SVM) classifier to the PCA plots \textbf{(Fig.2 E and F)}. Consistent with our observations from the PCA plots, we observed that the SVM was able to accurately classify Control samples versus AD and comorbid PDAD samples. However, SVM classifier performed substantially worse with PD samples. Based on these observations, we concluded that the PD samples do not exhibit noticeable variances in gene expression compared to Control samples.

\section{Linear modelling to identify differential expression}
\label{sec:line-modell-ident}

In order to identify differentially expressed genes between Control samples and disease-state samples, we utilized linear models. We  samples as covariates (with parameter coefficientsfor the control, AD, PD, and AD/PD samples) in order to determine the strength of association between each gene and the disease phenotypes. We used two separate linear modelling approaches. First, we modelled each trait as additive categorical random variables: 
\begin{align*}
E[Y^{i}|X^{i}] &= \beta_{Ctl} + \beta_{AD}x_{AD}^{i} + \beta_{PD}x_{PD}^{i} + \beta_{ADPD}x_{ADPD}^{i} \\  
\end{align*}
Where the $x^{i}s$ are indicator variables for the presence or absence of each disease-trait in a sample.Using this approach, we performed linear modelling on each gene, and obtained sample estimators $\hat{\beta}_{Ctl}, \hat{\beta}_{AD}, \hat{\beta}_{PD}, and \hat{\beta}_{ADPD}$. 

We also considered that the changes in gene expression values in the ADPD case may not simply reflect additive changes in from both AD and PD in a linear model. To model this, we considered the comorbid case as an interaction effect between both the AD and PD traits:
\begin{align*}
E[Y^{i}|X^{i}] &= \beta_{Ctl} + \beta_{AD}x_{AD}^{i} + \beta_{PD}x_{PD}^{i} + \beta_{ADPD}x_{AD}^{i}x_{PD}^{i} \\  
\end{align*}
Repeating the same analysis as in the additive case, we obtained sample estimators for the AD, PD, and ADPD cases.

\subsection{Volcano plots to identify differential expression}
\label{subsec:volc-plots-ident}

After obtaining sample estimators  $\hat{\beta}_{Ctl}, \hat{\beta}_{AD}, \hat{\beta}_{PD},$ and $\hat{\beta}_{ADPD}$ for each gene in the in Frontal Cortex and Anterior Cingulate Cyrus, we then computed the the log-fold change and p-value of the fold-change. We performed this calculation for each gene with the disease-state sample estimators against the Control sample estimator:
\begin{align*}
& log_{2}FC( \hat{\beta}_{Ctl},\hat{\beta}_{AD})		&Pval (\hat{ \beta}_{Ctl},\hat{\beta}_{AD}) \\  
& log_{2}FC(\hat{ \beta}_{Ctl},\hat{\beta}_{PD})		& Pval(\hat{ \beta}_{Ctl},\hat{\beta}_{PD}) \\  
& log_{2}FC( \hat{\beta}_{Ctl},\hat{\beta}_{ADPD})   		& Pval(\hat{ \beta}_{Ctl},\hat{\beta}_{ADPD}) \\  
\end{align*}

Next, we plotted our results using volcano plots. We defined a differential expressed gene as any gene expression value where the p-value was less than $\frac{0.05}{nGenes}$ and the $log_{2}$ fold-change was larger than $0.25$ \textbf{(Fig 3.A and B)}.

\section{Weighted correlation network analysis}
\label{sec:weight-corr-netw}

 Using the candidate differentially expressed genes for the PD, AD, and PD/AD disease phenotypes, we will apply weighted correlation network analysis in order to determine if the candidate genes exhibit interesting coexpression patterns. First, using the available WGNA R-package\cite{Langfelder2008}, we will determine whether there are interesting coexpression clusterings between differentially expressed genes for each phenotype. Next, we will assess the clustering size/structure and compare these properties between phenotypes.

\subsection{Analysis of coexpression clusterings}
\label{subsec:analys-coexpr-clust}

\subsubsection{Size and structure of clusterings}
\label{subsec:size-struct-clust}

\subsubsection{Comparison of clusters between phenotypes}
\label{subsec:comp-clust-betw}


\section{Biological functions of differentially expressed genes}
\label{sec:biol-funct-diff}

Using the PANTHER gene ontology database, we identify the functional classifications of the differential expressed genes. We will perform this analysis between all phenotypes in order to comment on genes that may have unique biological roles related to PD, AD, and PD/AD disease states.


\subsection{PANTHER gene ontology database}
\label{subsec:panth-gene-ontol}

The PANTHER project, which we used to identify the biological functions of the differentially expressed genes, has the following purpose\cite{PANTHER}:\\

\begin{blockquote}
  The PANTHER (protein annotation through evolutionary relationship) classification system (\url{http://www.pantherdb.org/}{http://www.pantherdb.org/}) is a comprehensive system that combines gene function, ontology, pathways and statistical analysis tools that enable biologists to analyze large-scale, genome-wide data from sequencing, proteomics or gene expression experiments. The system is built with 82 complete genomes organized into gene families and subfamilies, and their evolutionary relationships are captured in phylogenetic trees, multiple sequence alignments and statistical models (hidden Markov models or HMMs). Genes are classified according to their function in several different ways: families and subfamilies are annotated with ontology terms (Gene Ontology (GO) and PANTHER protein class), and sequences are assigned to PANTHER pathways.
\end{blockquote}

\subsection{Functional classifications of differentially expressed proteins in frontal cortex}
\label{subsec:funct-class-diff}


\subsubsection{Alzheimer's Disease versus Controls (Additive Model)}

\begin{itemize}
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D6893\%7CUniProtKB\%3DP10636}{P10636-4}: Microtubule-associated protein tau, associated with microtubule binding and neuron projection.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17056\%7CUniProtKB\%3DQ9Y2J0}{RPH3A}: Rabphilin-3A, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2318\%7CUniProtKB\%3DQ9HCH3}{CPNE5}: Copine-5, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20318\%7CUniProtKB\%3DQ9H4F8}{SMOC1}: SPARC-related modular calcium-binding protein 1, associated with the binding of calcium ions.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D4638\%7CUniProtKB\%3DP09211}{GSTP1}: Glutathione S-transferase P, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9099\%7CUniProtKB\%3DQ9UIW2}{PLXNA1}: Plexin-A1, associated with axon guidance mediated by semaphorins, nervous system development, signal transducer activity, receptor activity, GTPase activity, pyrophosphatase activity, and many others.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29393\%7CUniProtKB\%3DQ96Q06}{PLIN4}: Perilipin-4, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11444\%7CUniProtKB\%3DP61764}{STXBP1}: Syntaxin-binding protein 1, associated with synaptic vesicle exocytosis and trafficking (as part of synaptic transmission).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2451\%7CUniProtKB\%3DP48729}{CSNK1A1}: Casein kinase I isoform alpha, associated with protein kinase activity. Well known to be associated with Parkinson's disease.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D16753\%7CUniProtKB\%3DP30041}{PRDX6}: Peroxiredoxin-6, associated with peroxidase activity in the cytosol, part of homeostatic processes.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2033\%7CUniProtKB\%3DP78369}{CLDN10}: Claudin-10, a tight junction protein known to be found in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D8923\%7CUniProtKB\%3DO43175}{PHGDH}: D-3-phosphoglycerate dehydrogenase, associated with the synthesis of serine and glycine and oxidoreductase activity.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D19129\%7CUniProtKB\%3DQ9Y617}{PSAT1}: Phosphoserine aminotransferase, also associated with the synthesis of serine and glycine, as well as pyridoxal-5 phosphate synthesis and vitamin B6 metabolism.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2482\%7CUniProtKB\%3DP04080}{CSTB}: Cystatin-B, known to be a cysteine protease inhibitor.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D4288\%7CUniProtKB\%3DO95452}{GJB6}: Gap junction beta-6 protein, associated with gap junction channel activity in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D10661\%7CUniProtKB\%3DP31431}{SDC4}: Syndecan-4, a cytoskeletal protein involved in cell adhesion and the extracellular matrix, as well as membrane-bound signalling.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11280\%7CUniProtKB\%3DQ13501}{SQSTM1}: Sequestosome-1, known to be associated with protein binding in vacuoles in the cytoplasm.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D5246\%7CUniProtKB\%3DP04792}{HSPB1}: Heat shock protein beta-1, involved in multiple signalling pathways as well as sensory and in particular visual perception.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D18304\%7CUniProtKB\%3DQ14019}{COTL1}: Coactosin-like protein, involved in the intracellular actin cytoskeleton, in particular with the binding of actin as well as a cytoskeletal component itself.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D19663\%7CUniProtKB\%3DQ9UBI6}{GNG12}: Guanine nucleotide-binding protein G(I)/G(S)/G(O) subunit gamma-12, involved in GTPase activity, protein binding, and numerous signalling pathways.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20983\%7CUniProtKB\%3DQ8N987}{NECAB1}: N-terminal EF-hand calcium-binding protein 1, known to be found in the cytoplasm and involved in the regulation of cellular metabolism, given the naming presumably via the binding of calcium. Otherwise little else appears to be known.
\end{itemize}

\textbf{Comments:} First, it is a good validation of our methodology that it detected the differential expression of the tau proteins, given the extensive prior literature relating these proteins to Alzheimer's disease. It is also noteworthy that protein already well-known to be associated with Parkinson's disease, namely Casein kinase I isoform alpha, was found to be differentially expressed in the frontal cortex of Alzheimer's disease patients who did not also have Parkinson's. This is for two reasons: first, Parkinson's does not seem to affect the frontal cortex, so it is interesting that it might be involved with Alzheimer's in that region of the brain, and second, it provides support for the authors' conjecture that there may be structural similarity/relationship between the development of Alzheimer's and Parkinson's diseases.

As for some possible common themes that seem worth mentioning with regards to the biological functions of the differentially expressed proteins, these include calcium-binding, GTPase activity, synthesis of serine and glycine, signalling pathways, protein binding, cellular membrane functions, and the internal and external cytoskeletons.

Also, there were several proteins identified as differentially expressed whose function is still relatively unknown, including (but not necessarily limited to) Rabphilin-3A, Copine-5, Glutathione S-transferase P, and Perilipin-4. Our analysis strongly suggests that future research clarifying the biological function of these specific proteins could be relevant to understanding the pathology behind Alzheimer's disease.

\subsubsection{Parkinson's Disease versus Controls (Additive Model)}

No genes were differentially expressed. This is also a validation of our methodology, since it corresponds to previous work which suggests that there is no manifestation of Parkinson's in the frontal cortex.

\subsubsection{Comorbid Alzheimer's and Parkinson's Diseases versus Controls (Additive Model)}

\begin{itemize}
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D12684\%7CUniProtKB\%3DO15240}{O15240}: Neurosecretory protein VGF, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20318\%7CUniProtKB\%3DQ9H4F8}{Q9H4F8}: SPARC-related modular calcium-binding protein 1, associated with the binding of calcium ions.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9243\%7CUniProtKB\%3DO14829}{O14829}: Serine/threonine-protein phosphatase with EF-hands 1, associated with apoptosis and intracellular signalling.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17972\%7CUniProtKB\%3DQ9NPD7}{A0A087WWT2}: Neuritin, also known as \href{https://www.uniprot.org/uniprot/A0A087WWT2}{NRN1}, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9476\%7CUniProtKB\%3DQ92743}{Q92743}: Serine protease HTRA1, associated with serine-type proteolysis (peptide and protein breakdown).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D5246\%7CUniProtKB\%3DP04792}{P04792}: Heat shock protein beta-1, involved in multiple signalling pathways as well as sensory and in particular visual perception.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11280\%7CUniProtKB\%3DQ13501}{Q13501}: Sequestosome-1, known to be associated with protein binding in vacuoles in the cytoplasm.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29393\%7CUniProtKB\%3DQ96Q06}{Q96Q06}: Perilipin-4, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17056\%7CUniProtKB\%3DQ9Y2J0}{Q9Y2J0}: Rabphilin-3A, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D13564\%7CUniProtKB\%3DQ92563}{Q92563}: Testican-2, associated with calcium ion binding, and the inhibition of proteolysis.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2033\%7CUniProtKB\%3DP78369}{P78369}: Claudin-10,  a tight junction protein known to be found in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D964\%7CUniProtKB\%3DO75936}{O75936}: Gamma-butyrobetaine dioxygenase, known to be associated with the synthesis of certain vitamins.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17187\%7CUniProtKB\%3DQ99784}{Q99784}: Noelin, a phosphate ion receptor and transporter.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D13345\%7CUniProtKB\%3DQ14693}{Q14693}: Phosphatidate phosphatase LPIN1, known to be associated with the regulation of transcription.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D3978\%7CUniProtKB\%3DO75891}{O75891}: Cytosolic 10-formyltetrahydrofolate dehydrogenase, a catalyst for the transfer of electrons from one molecule to another (oxidation-reduction reactions).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D166\%7CUniProtKB\%3DO43707}{K7EJH8}: Alpha-actinin-4, also known as \href{https://www.uniprot.org/uniprot/K7EJH8}{ACTN4}, associated with the morphogenesis of the extracellular matrix/cytoskeleton.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D1470\%7CUniProtKB\%3DQ96RR4}{Q96RR4}: Calcium/calmodulin-dependent protein kinase 2, associated with calcium-mediated synaptic transmission.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29180\%7CUniProtKB\%3DQ9UPV7}{Q9UPV7}: Unnamed, also known as \href{https://www.uniprot.org/uniprot/Q9UPV7}{PHF24 (PHD Finger Protein 24))}, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D1063\%7CUniProtKB\%3DP30043}{P30043}: Flavin reductase (NADPH), another oxidation-reduction catalyst.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D8576\%7CUniProtKB\%3DQ15102}{Q15102}: Platelet-activating factor acetylhydrolase IB subunit gamma, specific function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20039\%7CUniProtKB\%3DP40123}{P40123}: Adenylyl cyclase-associated protein 2, known to be involved in the organization and regulation of the intracellular actin cytoskeleton in the cytoplasm.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D16280\%7CUniProtKB\%3DQ9NQ86}{Q9NQ86}: E3 ubiquitin-protein ligase TRIM36, specific function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9064\%7CUniProtKB\%3DQ9UPR0}{Q9UPR0}: Inactive phospholipase C-like protein 2, associated with GTPase regulation and several intracellular signalling pathways.
\end{itemize}

Some common themes include regulation and development of the actin cytoskeleton, oxidation-reduction reaction catalysts, and several of the categories mentioned above (e.g. calcium ion binding, GTPase regulators, signalling pathways, vitamin synthesis, protein binding, etc.).

The occurrence of several proteins in both this group as well as those differentially expressed with Alzheimer's (e.g. heat-shock protein beta-1, Sequestosome-1, SPARC-related modular calcium-binding protein 1) only could be seen to validate our methodology, since we would expect these two groups to have similar protein expression profiles. Similarly, the occurrence of the unknown function proteins Perilipin-4 and Rabphilin-3A as differentially expressed in both of these groups strongly argues in favor of follow-up studies investigating the function and structure of these proteins.

\subsubsection{Alzheimer's Disease versus Controls (Interaction Model)}


\begin{itemize}
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D6893\%7CUniProtKB\%3DP10636}{P10636}: Microtubule-associated protein tau, associated with microtubule binding and neuron projection.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20318\%7CUniProtKB\%3DQ9H4F8}{Q9H4F8}: SPARC-related modular calcium-binding protein 1, associated with the binding of calcium ions.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17972\%7CUniProtKB\%3DQ9NPD7}{A0A087WWT2}: also known as \href{https://www.uniprot.org/uniprot/A0A087WWT2}{Neuritin}, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D5246\%7CUniProtKB\%3DP04792}{P04792}: Heat shock protein beta-1, involved in multiple signalling pathways as well as sensory and in particular visual perception.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17056\%7CUniProtKB\%3DQ9Y2J0}{Q9Y2J0}: Rabphilin-3A, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11280\%7CUniProtKB\%3DQ13501}{Q13501}: Sequestosome-1, known to be associated with protein binding in vacuoles in the cytoplasm.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D10661\%7CUniProtKB\%3DP31431}{P31431}: Syndecan-4, a cytoskeletal protein involved in cell adhesion and the extracellular matrix, as well as membrane-bound signalling.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2033\%7CUniProtKB\%3DP78369}{P78369}:  Claudin-10,  a tight junction protein known to be found in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D4288\%7CUniProtKB\%3DO95452}{O95452}: Gap junction beta-6 protein, associated with gap junction channel activity in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29393\%7CUniProtKB\%3DQ96Q06}{Q96Q06}: Perilipin-4, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D19663\%7CUniProtKB\%3DQ9UBI6}{Q9UBI6}: Guanine nucleotide-binding protein G(I)/G(S)/G(O) subunit gamma-12, involved in GTPase activity, protein binding, and numerous signalling pathways.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D18304\%7CUniProtKB\%3DQ14019}{Q14019}: Coactosin-like protein, involved in the intracellular actin cytoskeleton, in particular with the binding of actin as well as a cytoskeletal component itself.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29167\%7CUniProtKB\%3DQ9Y2K5}{B5MCG9}: R3H domain-containing protein 2, also known as \href{https://www.uniprot.org/uniprot/B5MCG9}{R3HDM2}, function unknown in humans.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2482\%7CUniProtKB\%3DP04080}{P04080}: Cystatin-B, known to be a cysteine protease inhibitor.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D16753\%7CUniProtKB\%3DP30041}{P30041}: Peroxiredoxin-6, an enzyme which catalyzes the oxidation via hydrogen peroxide.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29180\%7CUniProtKB\%3DQ9UPV7}{Q9UPV7}: Unnamed, also known as \href{https://www.uniprot.org/uniprot/Q9UPV7}{PHF24 (PHD Finger Protein 24)}, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D19129\%7CUniProtKB\%3DQ9Y617}{Q9Y617}: Phosphoserine aminotransferase, also associated with the synthesis of serine and glycine, as well as pyridoxal-5 phosphate synthesis and vitamin B6 metabolism.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D8923\%7CUniProtKB\%3DO43175}{O43175}: D-3-phosphoglycerate dehydrogenase, associated with the synthesis of serine and glycine.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D4638\%7CUniProtKB\%3DP09211}{P09211}: Glutathione S-transferase P, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11444\%7CUniProtKB\%3DP61764}{P61764}: Syntaxin-binding protein 1, also known as \href{https://www.uniprot.org/uniprot/P61764}{STXBP1}, associated with synaptic vesicle exocytosis and trafficking (as part of synaptic transmission).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2451\%7CUniProtKB\%3DP48729}{P48729}: Also known as \href{https://www.uniprot.org/uniprot/P48729}{CSNK1A1 (Casein kinase I isoform alpha))}, associated with protein kinase activity. Well known to be associated with Parkinson's disease.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9099\%7CUniProtKB\%3DQ9UIW2}{Q9UIW2}: Also known as \href{https://www.uniprot.org/uniprot/Q9UIW2}{PLXNA1 (Plexin-A1)}, associated with axon guidance mediated by semaphorins, nervous system development, signal transducer activity, receptor activity, GTPase activity, pyrophosphatase activity, and many others.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20983\%7CUniProtKB\%3DQ8N987}{Q8N987}: N-terminal EF-hand calcium-binding protein 1, known to be found in the cytoplasm and involved in the regulation of cellular metabolism, given the naming presumably via the binding of calcium. Otherwise little else appears to be described in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2318\%7CUniProtKB\%3DQ9HCH3}{Q9HCH3}: Copine-5, function undescribed for humans in PANTHER.
\end{itemize}

We see an extremely large overlap between proteins already identified via the additive model as differentially expressed in either Alzheimer's patients or patients with comorbid Alzheimer's and Parkinson's, with the only exception being R3H domain-containing protein 2. Thus this seems to lend further support to the importance of these genes, if only to the extent that their being identified as differentially expressed does not appear contingent upon the exact assumptions of the linear model being used.

Also note that this model again reaffirms what is already known about Alzheimer's, namely that it's trademark manifestation in the frontal cortex occurs via the tau protein.

\subsubsection{Parkinson's Disease versus Controls (Interaction Model)}

No genes were differentially expressed. Again, this is arguably a validation of our methodology, since it corresponds to previous work which suggests that there is no manifestation of Parkinson's in the frontal cortex.

\subsubsection{Comorbid Alzheimer's and Parkinson's Diseases versus Controls (Interaction Model)}

\begin{itemize}
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D12684\%7CUniProtKB\%3DO15240}{O15240}: Neurosecretory protein VGF, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20318\%7CUniProtKB\%3DQ9H4F8}{Q9H4F8}: SPARC-related modular calcium-binding protein 1, associated with the binding of calcium ions.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9243\%7CUniProtKB\%3DO14829}{O14829}: Serine/threonine-protein phosphatase with EF-hands 1, associated with apoptosis and intracellular signalling.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17972\%7CUniProtKB\%3DQ9NPD7}{A0A087WWT2}: Neuritin, also known as \href{https://www.uniprot.org/uniprot/A0A087WWT2}{NRN1}, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9476\%7CUniProtKB\%3DQ92743}{Q92743}: Serine protease HTRA1, associated with serine-type proteolysis (peptide and protein breakdown).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D5246\%7CUniProtKB\%3DP04792}{P04792}: Heat shock protein beta-1, involved in multiple signalling pathways as well as sensory and in particular visual perception.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11280\%7CUniProtKB\%3DQ13501}{Q13501}: Sequestosome-1, known to be associated with protein binding in vacuoles in the cytoplasm.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29393\%7CUniProtKB\%3DQ96Q06}{Q96Q06}: Perilipin-4, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17056\%7CUniProtKB\%3DQ9Y2J0}{Q9Y2J0}: Rabphilin-3A, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D13564\%7CUniProtKB\%3DQ92563}{Q92563}: Testican-2, associated with calcium ion binding, and the inhibition of proteolysis.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2033\%7CUniProtKB\%3DP78369}{P78369}: Claudin-10,  a tight junction protein known to be found in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D964\%7CUniProtKB\%3DO75936}{O75936}: Gamma-butyrobetaine dioxygenase, known to be associated with the synthesis of certain vitamins.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17187\%7CUniProtKB\%3DQ99784}{Q99784}: Noelin, a phosphate ion receptor and transporter.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D13345\%7CUniProtKB\%3DQ14693}{Q14693}: Phosphatidate phosphatase LPIN1, known to be associated with the regulation of transcription.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D3978\%7CUniProtKB\%3DO75891}{O75891}: Cytosolic 10-formyltetrahydrofolate dehydrogenase, a catalyst for the transfer of electrons from one molecule to another (oxidation-reduction reactions).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D166\%7CUniProtKB\%3DO43707}{K7EJH8}: Alpha-actinin-4, also known as \href{https://www.uniprot.org/uniprot/K7EJH8}{ACTN4}, associated with the morphogenesis of the extracellular matrix/cytoskeleton.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D1470\%7CUniProtKB\%3DQ96RR4}{Q96RR4}: Calcium/calmodulin-dependent protein kinase 2, associated with calcium-mediated synaptic transmission.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29180\%7CUniProtKB\%3DQ9UPV7}{Q9UPV7}: Unnamed, also known as \href{https://www.uniprot.org/uniprot/Q9UPV7}{PHF24 (PHD Finger Protein 24)}, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D1063\%7CUniProtKB\%3DP30043}{P30043}: Flavin reductase (NADPH), another oxidation-reduction catalyst.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D8576\%7CUniProtKB\%3DQ15102}{Q15102}: Platelet-activating factor acetylhydrolase IB subunit gamma, specific function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20039\%7CUniProtKB\%3DP40123}{P40123}: Adenylyl cyclase-associated protein 2, known to be involved in the organization and regulation of the intracellular actin cytoskeleton in the cytoplasm.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D16280\%7CUniProtKB\%3DQ9NQ86}{Q9NQ86}: E3 ubiquitin-protein ligase TRIM36, specific function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9064\%7CUniProtKB\%3DQ9UPR0}{Q9UPR0}:  Inactive phospholipase C-like protein 2, associated with GTPase regulation and several intracellular signalling pathways.
\end{itemize}

Even though some of the results are given via gene ID instead of protein ID or vice versa, ultimately the results here are literally identically the same as those for the additive model. This suggests that the two models also should have given identical output for the Alzheimer's only group as well (they gave identical output for the Parkinson's only group too), which strongly suggests that we may have made an error in our analysis (which unfortunately due to time constraints cannot be addressed).

\subsection{Comparisons of differentially expressed proteins between models and phenotypes}
\label{sec:comp-diff-expr}

\subsubsection{Proteins identified in Alzheimer's by the additive versus the interaction model}
\label{sec:prot-ident-alzh}

\paragraph{Common proteins}

\begin{itemize}
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D6893\%7CUniProtKB\%3DP10636}{P10636}: Microtubule-associated protein tau, associated with microtubule binding and neuron projection.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17056\%7CUniProtKB\%3DQ9Y2J0}{Q9Y2J0}: Rabphilin-3A, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2318\%7CUniProtKB\%3DQ9HCH3}{Q9HCH3}: Copine-5, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20318\%7CUniProtKB\%3DQ9H4F8}{Q9H4F8}: SPARC-related modular calcium-binding protein 1, associated with the binding of calcium ions.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D4638\%7CUniProtKB\%3DP09211}{P09211}: Glutathione S-transferase P, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9099\%7CUniProtKB\%3DQ9UIW2}{Q9UIW2}: Also known as \href{https://www.uniprot.org/uniprot/Q9UIW2}{PLXNA1 (Plexin-A1)}, associated with axon guidance mediated by semaphorins, nervous system development, signal transducer activity, receptor activity, GTPase activity, pyrophosphatase activity, and many others.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29393\%7CUniProtKB\%3DQ96Q06}{Q96Q06}: Perilipin-4, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11444\%7CUniProtKB\%3DP61764}{P61764}: Syntaxin-binding protein 1, also known as \href{https://www.uniprot.org/uniprot/P61764}{STXBP1}, associated with synaptic vesicle exocytosis and trafficking (as part of synaptic transmission).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2451\%7CUniProtKB\%3DP48729}{P48729}: Also known as \href{https://www.uniprot.org/uniprot/P48729}{CSNK1A1 (Casein kinase I isoform alpha))}, associated with protein kinase activity. Well known to be associated with Parkinson's disease.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D16753\%7CUniProtKB\%3DP30041}{P30041}: Peroxiredoxin-6, an enzyme which catalyzes the oxidation via hydrogen peroxide.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2033\%7CUniProtKB\%3DP78369}{P78369}: Claudin-10,  a tight junction protein known to be found in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D8923\%7CUniProtKB\%3DO43175}{O43175}: D-3-phosphoglycerate dehydrogenase, associated with the synthesis of serine and glycine.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D19129\%7CUniProtKB\%3DQ9Y617}{Q9Y617}: Phosphoserine aminotransferase, also associated with the synthesis of serine and glycine, as well as pyridoxal-5 phosphate synthesis and vitamin B6 metabolism.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2482\%7CUniProtKB\%3DP04080}{P04080}: Cystatin-B, known to be a cysteine protease inhibitor.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D4288\%7CUniProtKB\%3DO95452}{O95452}: Gap junction beta-6 protein, associated with gap junction channel activity in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D10661\%7CUniProtKB\%3DP31431}{P31431}: Syndecan-4, a cytoskeletal protein involved in cell adhesion and the extracellular matrix, as well as membrane-bound signalling.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11280\%7CUniProtKB\%3DQ13501}{Q13501}: Sequestosome-1, known to be associated with protein binding in vacuoles in the cytoplasm.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D5246\%7CUniProtKB\%3DP04792}{P04792}: Heat shock protein beta-1, involved in multiple signalling pathways as well as sensory and in particular visual perception.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D18304\%7CUniProtKB\%3DQ14019}{Q14019}: Coactosin-like protein, involved in the intracellular actin cytoskeleton, in particular with the binding of actin as well as a cytoskeletal component itself.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D19663\%7CUniProtKB\%3DQ9UBI6}{Q9UBI6}: Guanine nucleotide-binding protein G(I)/G(S)/G(O) subunit gamma-12, involved in GTPase activity, protein binding, and numerous signalling pathways.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20983\%7CUniProtKB\%3DQ8N987}{Q8N987}: N-terminal EF-hand calcium-binding protein 1, known to be found in the cytoplasm and involved in the regulation of cellular metabolism, given the naming presumably via the binding of calcium. Otherwise little else appears to be described in PANTHER.
\end{itemize}

\paragraph{Different proteins}

\paragraph{Identified by interaction model but not additive model}

\begin{itemize}
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17972\%7CUniProtKB\%3DQ9NPD7}{A0A087WWT2}: Neuritin, also known as \href{https://www.uniprot.org/uniprot/A0A087WWT2}{NRN1}, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29167\%7CUniProtKB\%3DQ9Y2K5}{B5MCG9}: R3H domain-containing protein 2, also known as \href{https://www.uniprot.org/uniprot/B5MCG9}{R3HDM2}, function unknown in humans.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29180\%7CUniProtKB\%3DQ9UPV7}{Q9UPV7}: Unnamed, also known as \href{https://www.uniprot.org/uniprot/Q9UPV7}{PHF24 (PHD Finger Protein 24))}, function undescribed for humans in PANTHER.
\end{itemize}

\paragraph{Identified by interaction model but not additive model}

None.

\subsubsection{Differentially expressed proteins in comorbid versus non-comorbid Alzheimer's}
\label{sec:diff-expr-prot}

\paragraph{Common proteins}

\begin{itemize}
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17056\%7CUniProtKB\%3DQ9Y2J0}{Q9Y2J0}: Rabphilin-3A, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20318\%7CUniProtKB\%3DQ9H4F8}{Q9H4F8}: SPARC-related modular calcium-binding protein 1, associated with the binding of calcium ions.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29393\%7CUniProtKB\%3DQ96Q06}{Q96Q06}: Perilipin-4, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2033\%7CUniProtKB\%3DP78369}{P78369}: Claudin-10,  a tight junction protein known to be found in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11280\%7CUniProtKB\%3DQ13501}{Q13501}: Sequestosome-1, known to be associated with protein binding in vacuoles in the cytoplasm.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D5246\%7CUniProtKB\%3DP04792}{P04792}: Heat shock protein beta-1, involved in multiple signalling pathways as well as sensory and in particular visual perception.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17972\%7CUniProtKB\%3DQ9NPD7}{A0A087WWT2}: Neuritin, also known as \href{https://www.uniprot.org/uniprot/A0A087WWT2}{NRN1}, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29180\%7CUniProtKB\%3DQ9UPV7}{Q9UPV7}: Unnamed, also known as \href{https://www.uniprot.org/uniprot/Q9UPV7}{PHF24 (PHD Finger Protein 24))}, function undescribed for humans in PANTHER.
\end{itemize}

\paragraph{Different proteins}

\paragraph{In comorbid but not non-comorbid}

\begin{itemize}
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D12684\%7CUniProtKB\%3DO15240}{O15240}: Neurosecretory protein VGF, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9243\%7CUniProtKB\%3DO14829}{O14829}: Serine/threonine-protein phosphatase with EF-hands 1, associated with apoptosis and intracellular signalling.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9476\%7CUniProtKB\%3DQ92743}{Q92743}: Serine protease HTRA1, associated with serine-type proteolysis (peptide and protein breakdown).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D13564\%7CUniProtKB\%3DQ92563}{Q92563}: Testican-2, associated with calcium ion binding, and the inhibition of proteolysis.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D964\%7CUniProtKB\%3DO75936}{O75936}: Gamma-butyrobetaine dioxygenase, known to be associated with the synthesis of certain vitamins.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D17187\%7CUniProtKB\%3DQ99784}{Q99784}: Noelin, a phosphate ion receptor and transporter.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D13345\%7CUniProtKB\%3DQ14693}{Q14693}: Phosphatidate phosphatase LPIN1, known to be associated with the regulation of transcription.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D3978\%7CUniProtKB\%3DO75891}{O75891}: Cytosolic 10-formyltetrahydrofolate dehydrogenase, a catalyst for the transfer of electrons from one molecule to another (oxidation-reduction reactions).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D166\%7CUniProtKB\%3DO43707}{K7EJH8}: Alpha-actinin-4, also known as \href{https://www.uniprot.org/uniprot/K7EJH8}{ACTN4}, associated with the morphogenesis of the extracellular matrix/cytoskeleton.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D1470\%7CUniProtKB\%3DQ96RR4}{Q96RR4}: Calcium/calmodulin-dependent protein kinase 2, associated with calcium-mediated synaptic transmission.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D1063\%7CUniProtKB\%3DP30043}{P30043}: Flavin reductase (NADPH), another oxidation-reduction catalyst.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D8576\%7CUniProtKB\%3DQ15102}{Q15102}: Platelet-activating factor acetylhydrolase IB subunit gamma, specific function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20039\%7CUniProtKB\%3DP40123}{P40123}: Adenylyl cyclase-associated protein 2, known to be involved in the organization and regulation of the intracellular actin cytoskeleton in the cytoplasm.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D16280\%7CUniProtKB\%3DQ9NQ86}{Q9NQ86}: E3 ubiquitin-protein ligase TRIM36, specific function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9064\%7CUniProtKB\%3DQ9UPR0}{Q9UPR0}:  Inactive phospholipase C-like protein 2, associated with GTPase regulation and several intracellular signalling pathways.
\end{itemize}

\paragraph{In non-comorbid but not in comorbid}

\begin{itemize}
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D6893\%7CUniProtKB\%3DP10636}{P10636}: Microtubule-associated protein tau, associated with microtubule binding and neuron projection.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2318\%7CUniProtKB\%3DQ9HCH3}{Q9HCH3}: Copine-5, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D4638\%7CUniProtKB\%3DP09211}{P09211}: Glutathione S-transferase P, function undescribed for humans in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D9099\%7CUniProtKB\%3DQ9UIW2}{Q9UIW2}: Also known as \href{https://www.uniprot.org/uniprot/Q9UIW2}{PLXNA1 (Plexin-A1)}, associated with axon guidance mediated by semaphorins, nervous system development, signal transducer activity, receptor activity, GTPase activity, pyrophosphatase activity, and many others.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D11444\%7CUniProtKB\%3DP61764}{P61764}: Syntaxin-binding protein 1, also known as \href{https://www.uniprot.org/uniprot/P61764}{STXBP1}, associated with synaptic vesicle exocytosis and trafficking (as part of synaptic transmission).
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2451\%7CUniProtKB\%3DP48729}{P48729}: Also known as \href{https://www.uniprot.org/uniprot/P48729}{CSNK1A1 (Casein kinase I isoform alpha))}, associated with protein kinase activity. Well known to be associated with Parkinson's disease.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D16753\%7CUniProtKB\%3DP30041}{P30041}: Peroxiredoxin-6, an enzyme which catalyzes the oxidation via hydrogen peroxide.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D8923\%7CUniProtKB\%3DO43175}{O43175}: D-3-phosphoglycerate dehydrogenase, associated with the synthesis of serine and glycine.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D19129\%7CUniProtKB\%3DQ9Y617}{Q9Y617}: Phosphoserine aminotransferase, also associated with the synthesis of serine and glycine, as well as pyridoxal-5 phosphate synthesis and vitamin B6 metabolism.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D2482\%7CUniProtKB\%3DP04080}{P04080}: Cystatin-B, known to be a cysteine protease inhibitor.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D4288\%7CUniProtKB\%3DO95452}{O95452}: Gap junction beta-6 protein, associated with gap junction channel activity in the plasma membrane.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D10661\%7CUniProtKB\%3DP31431}{P31431}: Syndecan-4, a cytoskeletal protein involved in cell adhesion and the extracellular matrix, as well as membrane-bound signalling.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D18304\%7CUniProtKB\%3DQ14019}{Q14019}: Coactosin-like protein, involved in the intracellular actin cytoskeleton, in particular with the binding of actin as well as a cytoskeletal component itself.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D19663\%7CUniProtKB\%3DQ9UBI6}{Q9UBI6}: Guanine nucleotide-binding protein G(I)/G(S)/G(O) subunit gamma-12, involved in GTPase activity, protein binding, and numerous signalling pathways.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D20983\%7CUniProtKB\%3DQ8N987}{Q8N987}: N-terminal EF-hand calcium-binding protein 1, known to be found in the cytoplasm and involved in the regulation of cellular metabolism, given the naming presumably via the binding of calcium. Otherwise little else appears to be described in PANTHER.
\item \href{http://www.pantherdb.org/genes/gene.do?acc=HUMAN\%7CHGNC\%3D29167\%7CUniProtKB\%3DQ9Y2K5}{B5MCG9}: R3H domain-containing protein 2, also known as \href{https://www.uniprot.org/uniprot/B5MCG9}{R3HDM2}, function unknown in humans.
\end{itemize}



\pagebreak

\bibliographystyle{siam}
\bibliography{bibliography}
\addcontentsline{toc}{section}{References}

\end{document}

